Linear response theory for core set identification

### 2012-08-05 writedown/linear.response/langevin.tex
fix bug
fix bug of the text
add tilt result of the gneral response theory

  \frac 1{2\sigma}\int_0^t

@@

  \frac 1{2\sigma}\int_0^\tau

@@

  \frac 1{\sigma}

@@

@@

  \Delta s_j^{i-1}\Delta s_k^{i-1}G_j[\vect X_s]G_k[\vect X_s]

@@

@@

  \big\}^2

@@

@@

@@

@@

@@

first order approximation, and the last two lines are the

@@

@@

See Fig. \ref{fig:tmp2} and \ref{fig:tmp3} for numerical result.  Both
the direct non-equilibrium simulation and the linear response
approximation are presented. Time slices $t = 0$, 10, 15 and 20
\textsf{ps} are shown.  When the perturbation is small,
i.e. $F_e^{\textrm{max}} = 2$, the direct non-equilibrium simulation
and the linear response results are accurately consistent. As the
perturbation grows stronger, the left well becomes less stable, while
the right well becomes more stable.  When the perturbation is big,
i.e. $F_e^{\textrm{max}} = 4$, the linear response results are no
longer precise. When $t\geq 10$ \textsf{ps}, the left well basically
disappears, however, the linear response calculation presents
artifical occilation at the right well.

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]
  {figs/tilt.warm020.str2.0.nst1e09.smallgrid/fig-2d.eps}
  \caption{The plot of $\Delta\mt_\tau f(\vect x,t)$  under perturbation of
    $F_e^{\textrm{max}} = 2$.
    Upper row: the direct non-equilibrium simulation. Lower row: the
    results of linear response formula~\eqref{eqn:core-identify-approx-2}.
  }
  \label{fig:tmp2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]
  {figs/tilt.warm020.str4.0.nst1e09.smallgrid/fig-2d.eps}
  \caption{The plot of $\Delta\mt_\tau f(\vect x,t)$  under perturbation of
    $F_e^{\textrm{max}} = 4$.  Upper row: the direct non-equilibrium
    simulation. Lower row: the results of linear response
    formula~\eqref{eqn:core-identify-approx-2}.  }
  \label{fig:tmp3}
\end{figure}

@@

In this splitting single-well potential example, the unperturbed
potential is simply the harmonic potential given by:
\begin{align}
  U(\vect q) = \frac12\,k\,\vect q^2 
\end{align}
Here $k = 8$~$\textsf{kJ} / (\textsf{mol nm}^2)$.
Notice at room temperature $300\ \textsf{K}$, $k_BT = 2.48$~\textsf{kJ/mol}.
See the red line in Fig.~\ref{fig:tmp4}.
%$\textsf{kJ} / (\textsf{mol nm}^4)}$
The perturbation is again given by
\begin{align}
  \vect C(\vect p, \vect q) = 0; \qquad
  \vect D(\vect p, \vect q) = -\nabla_{\vect q} V(\vect q) 
\end{align}
where $V(\vect q)$ is a Gaussian type potential:
\begin{align}
  V(\vect q) = \frac{1}{\sqrt{2\pi \sigma^2}}
  \exp\Big\{-\frac{\vect q^2}{2\sigma^2}\Big\}
\end{align}
we use $\sigma = 0.16$~\textsf{nm}. Please see Fig~\ref{fig:tmp4}.
For the results, please see Fig.~\ref{fig:tmp5} -- Fig.~\ref{fig:tmp6}.
\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]
  {figs/split.warm020.str1.0.nst1e09.smallgrid.more/fig-2d.eps}
  \caption{The plot of $\Delta\mt_\tau f(\vect x,t)$  under perturbation of
    $F_e^{\textrm{max}} = 1.0$.
    Upper row: the direct non-equilibrium simulation. Lower row: the
    results of linear response formula~\eqref{eqn:core-identify-approx-2}.
  }
  \label{fig:tmp5}
\end{figure}

@@

>>>>

  \frac 1{2\sigma^2}\int_0^t

@@

  \frac 1{2\sigma^2}\int_0^\tau

@@

@@

  % \frac12
  % \sum_{j,k=1}^\infty
  % \Delta s_j^{i-1} \Delta s_k^{i-1}H_{jk}[\vect X_s]

@@

  G_j[\vect X_s]G_k[\vect X_s] - H_{jk}[\vect X_s]

@@

  % \frac12[\Delta F_e^{i-1}(t)]^2
  % H_{00}[\vect X_\eta]

@@

  G^2_0[\vect X_\eta] - H_{00}[\vect X_\eta]

@@

  G^2_0[\vect X_s] - 

@@

  % +
  % \frac12[\Delta F_e^{i-1}(t)]^2
  % \big\langle
  % \big\{G_{0}[\vect X_\eta]\big\}^2
  % \big\rangle_{0,t,\tau}^{i-1}

@@

  G_j[\vect X_s] G_k[\vect X_s] - 

@@

  % +
  % \frac 12
  % \sum_{j,k=1}^\infty
  % \Delta s_j^{i-1}\Delta s_k^{i-1}
  % \big\langle
  % G_{j}[\vect X_s] G_k[\vect X_s]
  % \big\rangle_{0,t,\tau}^{i-1}

@@

first order approximation, and the last three lines are the

@@

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]
  {figs/fig-tilt-str2-2d-more.eps}
  \caption{The plot of $\Delta\mt_\tau f(\vect x,t)$  under perturbation of
    $F_e^{\textrm{max}} = 2$.
    The 1st row: the direct non-equilibrium
    simulation. The 2nd row: the results of linear response
    formula~\eqref{eqn:core-identify-approx-2}.
    The 3rd row: the results of response
    formula~\eqref{eqn:pert-approx-1} and \eqref{eqn:pert-approx-2}.
    The order is 2, the reference state is $F_e^{\textrm{max}} = 0$, i.e.
    the equilibrium state.
  }
  \label{fig:tmp2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]
  {figs/fig-tilt-str4-2d-more.eps}
  \caption{The plot of $\Delta\mt_\tau f(\vect x,t)$  under perturbation of
    $F_e^{\textrm{max}} = 4$.  The 1st row: the direct non-equilibrium
    simulation. The 2nd row: the results of linear response
    formula~\eqref{eqn:core-identify-approx-2}.
    The 3rd row: the results of response
    formula~\eqref{eqn:pert-approx-1} and \eqref{eqn:pert-approx-2}.
    The order is 2, the reference state is $F_e^{\textrm{max}} = 0$, i.e.
    the equilibrium state.
    The 4th row: the results of response
    formula~\eqref{eqn:pert-approx-1} and \eqref{eqn:pert-approx-2}.
    The order is 1, the reference state is $F_e^{\textrm{max}} = 2$.
  }
  \label{fig:tmp3}
\end{figure}

@@

See Fig. \ref{fig:tmp2} and \ref{fig:tmp3} for numerical result.  Both
the direct non-equilibrium simulation and the response
approximations are presented. Time slices $t = 0$, 10, 15 and 20
\textsf{ps} are shown.  When the perturbation is small,
i.e. $F_e^{\textrm{max}} = 2$, the direct non-equilibrium simulation
and the linear response results are accurately consistent.
The 2nd order response formula~\eqref{eqn:pert-approx-1} and
\eqref{eqn:pert-approx-2} are even better, but the numerical error
is bigger.
As the
perturbation grows stronger, the left well becomes less stable, while
the right well becomes more stable.  When the perturbation is big,
i.e. $F_e^{\textrm{max}} = 4$, the linear response result is no
longer precise.
When $t\geq 20$ \textsf{ps}, the left well basically
disappears, however, the linear response calculation presents
artifical occilation at the right well.
The 2nd order response also has artifical effect, and the numerical
uncertainty is high.
The 4th rwo of Fig.~\ref{fig:tmp3} presents the 1st order result of the
response formula~\eqref{eqn:pert-approx-1} and
\eqref{eqn:pert-approx-2}, with
respect to the reference state $F_e^{\textrm{max}} = 2$. The result
is impressively improved compared with the linear response with respect to the
equilibrium state.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.95\textwidth]
  {figs/split.warm020.str1.0.nst1e09.smallgrid.more/fig-2d.eps}
  \caption{The plot of $\Delta\mt_\tau f(\vect x,t)$  under perturbation of
    $F_e^{\textrm{max}} = 1.0$.
    Upper row: the direct non-equilibrium simulation. Lower row: the
    results of linear response formula~\eqref{eqn:core-identify-approx-2}.
  }
  \label{fig:tmp5}
\end{figure}

@@

In this splitting single-well potential example, the unperturbed
potential is simply the harmonic potential given by:
\begin{align}
  U(\vect q) = \frac12\,k\,\vect q^2 
\end{align}
Here $k = 8$~$\textsf{kJ} / (\textsf{mol nm}^2)$.
Notice at room temperature $300\ \textsf{K}$, $k_BT = 2.48$~\textsf{kJ/mol}.
See the red line in Fig.~\ref{fig:tmp4}.
%$\textsf{kJ} / (\textsf{mol nm}^4)}$
The perturbation is again given by
\begin{align}
  \vect C(\vect p, \vect q) = 0; \qquad
  \vect D(\vect p, \vect q) = -\nabla_{\vect q} V(\vect q) 
\end{align}
where $V(\vect q)$ is a Gaussian type potential:
\begin{align}
  V(\vect q) = \frac{1}{\sqrt{2\pi \sigma^2}}
  \exp\Big\{-\frac{\vect q^2}{2\sigma^2}\Big\}
\end{align}
we use $\sigma = 0.16$~\textsf{nm}. Please see Fig~\ref{fig:tmp4}.
For the results, please see Fig.~\ref{fig:tmp5} -- Fig.~\ref{fig:tmp6}.
